Static Race Detection in OS Kernels by Mining Locking Rules

### 2023-08-04 5.evaluation.tex
Add some evaluation results

\begin{table}[tbph]
	\tablecaption{Detection results of Linux 6.2.}
	\label{tbl_bug_detection}
	\renewcommand{\arraystretch}{1}
	\setlength\tabcolsep{2pt}
	\noindent{\scriptsize
		\begin{center}
			\begin{tabular}{p{1.5cm}|l|c}
				\hline
				\multicolumn{2}{c|}{\textbf{Description}} & \textbf{\sys}  
				\\ \hline
				\multirow{2}{1.5cm}{\textbf{{\em Code analysis}}} & 
				Source files (analyzed/all) & xxxK/xxxK
				\\ \cline{2-3}
				& Source code lines (analyzed/all) & xxxM/xxxM 
				\\ \cline{2-3}
				\hline
				\multirow{2}{1.5cm}{\textbf{{\em Locking-rule mining}}} & 
				Variables in key fields / total variables& 
				\\ \cline{2-3}
				& Mined locking rules &
				\\ \cline{2-3}
				\hline
				\multirow{2}{1.5cm}{\textbf{{\em Data race detection}}} & 
				Detected data races (real / all) & 273 / 341
				\\ \cline{2-3}
				& Dropped data races by lock-usage analysis & 63
				\\ \cline{2-3}
				\hline
				\multirow{4}{1.5cm}{\textbf{{\em Harmfulness estimation}}}
				& Null-pointer dereference (confirmed / all) & 15 / 20
				\\ \cline{2-3}
				& Data inconsistency (confirmed / all) & 7 / 10
				\\ \cline{2-3}
				& Double fetch (confirmed / all) & 10 / 57
				\\ \cline{2-3}
				& Total harmful data races (confirmed / all) & 32 / 87
				\\ \cline{2-3}
				\hline
				\multirow{3}{1.5cm}{\textbf{{\em Time usage}}} & 
				Key-field extraction & 
				\\ \cline{2-3}
				& Data-race detection &
				\\ \cline{2-3}
				& Total time &
				\\ \cline{2-3}
				\hline
			\end{tabular}
	\end{center}}
\end{table}

@@

\PP{Code analysis.} \sys can scale to large code bases of OS kernels, and it in 
total analyzes xxxM lines of code in xxxK source code files within xxx hours. 
The remaining xxxM lines of code in xxxK source files are not analyzed, as they 
are not enabled by the {\em allyesconfig} for the x86-64 architecture.

\PP{Locking-rule mining.} An OS kernel has a large code base with numerous 
variables. Handling all variables when mining locking rules can introduce much 
overhead. However, we observe that the variable that is accessed and the lock 
to protect the access often exist in the same data structure. Based on this 
observation, our locking-rule mining method extracts key fields by finding 
whether there exists any access to it that is protected by a lock stored in the 
same data structure. This method drops xxx\% variables (xxx out xxx) that need 
to be handled when mining locking rules, and thus can reduce overhead 
significantly. After extracting key fields, our locking-rule mining method 
collects all accesses to these key fields, and then deduces locking rules based 
on statistics. In this paper, given a data structure field, we set the 
threshold of the ratio of accesses protected by a specific lock to all accesses 
to 0.6. Our alias-aware rule mining method can drop many false rules and thus 
only mines xxx locking rules, which can effectively reduce false data races.

>>>>

\begin{table}[tbph]
	\tablecaption{Detection results of Linux 6.2.}
	\label{tbl_bug_detection}
	\renewcommand{\arraystretch}{1}
	\setlength\tabcolsep{2pt}
	\noindent{\scriptsize
		\begin{center}
			\begin{tabular}{p{1.5cm}|l|c}
				\hline
				\multicolumn{2}{c|}{\textbf{Description}} & \textbf{\sys}  
				\\ \hline
				\multirow{2}{1.5cm}{\textbf{{\em Code analysis}}} & 
				Source files (analyzed/all) & 22,537 / 32,328
				\\ \cline{2-3}
				& Source code lines (analyzed/all) & 13,686K / 16,646K 
				\\ \cline{2-3}
				\hline
				\multirow{3}{1.5cm}{\textbf{{\em Locking-rule mining}}} & 
				Extracted key fields & 23,074
				\\ \cline{2-3}
				& Handled variables (variables in key fields / total 
				variables)  & 23.2M / 281.0M
				\\ \cline{2-3}
				& Mined locking rules & 2,757
				\\ \cline{2-3}
				\hline
				\multirow{2}{1.5cm}{\textbf{{\em Data race detection}}} & 
				Detected data races (real / all) & 273 / 341
				\\ \cline{2-3}
				& Dropped data races by lock-usage analysis & 63
				\\ \cline{2-3}
				\hline
				\multirow{4}{1.5cm}{\textbf{{\em Harmfulness estimation}}}
				& Null-pointer dereference (confirmed / all) & 15 / 20
				\\ \cline{2-3}
				& Data inconsistency (confirmed / all) & 7 / 10
				\\ \cline{2-3}
				& Double fetch (confirmed / all) & 10 / 57
				\\ \cline{2-3}
				& Total harmful data races (confirmed / all) & 32 / 87
				\\ \cline{2-3}
				\hline
				\multirow{4}{1.5cm}{\textbf{{\em Time usage}}} & 
				Key-field extraction & 
				\\ \cline{2-3} 
				& Field-access collection & 
				\\ \cline{2-3}
				& Data-race detection and estimation &
				\\ \cline{2-3}
				& Total time & 772m
				\\ \cline{2-3}
				\hline
			\end{tabular}
	\end{center}}
\end{table}

@@

\PP{Code analysis.} \sys can scale to large code bases of OS kernels, and it 
totally analyzes 13.7M lines of code in 22.5K source files within 12.9 hours. 
The remaining 3.0M lines of code in 9.8K source files are not analyzed, as they 
are not enabled by {\em allyesconfig} for the x86-64 architecture.

\PP{Locking-rule mining.} An OS kernel has a large code base with numerous 
variables. Handling all variables when mining locking rules can introduce much 
overhead. However, we observe that the variable that is accessed and the lock 
to protect the access often exist in the same data structure. Based on this 
observation, our locking-rule mining method extracts key fields by finding 
whether there exists any access to it that is protected by a lock stored in the 
same data structure. This method extracts 23.1K key fields and drops 91.7\% 
variables (23.2M out 281.0M) that need to be handled when mining locking rules, 
and thus can reduce overhead significantly. After extracting key fields, our 
locking-rule mining method collects all accesses to these key fields, and then 
deduces locking rules based on statistics. In this paper, given a data 
structure field, we set the threshold of the ratio of accesses protected by a 
specific lock to all accesses to 0.6. Our alias-aware rule mining method can 
drop many false rules and thus only mines 2,757 locking rules, which can 
effectively reduce false data races.
